\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 trunk/europa-basics.tex
citations added to europa text

{\footnotesize
  \begin{quote}
[Planning] \emph{is an abstract, explicit deliberation process that chooses and
organizes actions by anticipating their expected outcomes. This
deliberation aims at achieving as best as possible some prestated
objectives. Automated planning is an area of Artificial Intelligence
(AI) that studies this deliberation process computationally.} -- from
\textbf{Automated Planning Theory and Practice} by Ghallab, Nau and
Traverso \cite{ghallab04} 
\end{quote}
}

@@

Arc Consistency and other, more stringent consistency definitions can
be used to efficiently prove that a \textsf{CP} problem is
unsatisfiable. However, they generally cannot prove that a \textsf{CP}
problem is satisfiable and provide specific variable assignments that
constitute solutions. For that, search algorithms like global
backtracking \comment{citation needed} or local search are used; these
use consistency as an efficient way to prune the search space
\cite{cp06}. In theory, solving a \textsf{CP} problem is NP-Hard
\cite{ghallab04}, but often very efficient in practice using a number
of consistency and search algorithms that are well understood.

@@

The most common planning formulations use a propositional
representation, where the state of the world is represented by a set
of propositions (statements that can be true or false), and operators
change the truth values of these propositions \cite{gen87}. Although
these formulations are powerful and have allowed researchers to
develop numerous contributions in automated planning, there are many
classes of problem domains that are difficult to represent using this
formalism. In particular, it is hard to represent time, resources,

% mutual exclusion and concurrency using propositions
% \cite{ghallab04}. While CSP representations have traditionally had an
% edge in formulating and representing planning problems,
% % It is straightforward to represent and reason about all of
% % those elements using a CSP representation, as a result there has been
% % some work on doing automated planning while taking advantage of CSP
% % (TODO: ref). Traditionally, the entire planning problem is translated
% % into a CSP and then solved using traditional CSP methods, this
% leading to a formulation where action choices and relationships are
% represented as variables and/or constraints, there are at least two
% major drawbacks:

mutual exclusion and concurrency using propositions
\comment{ghallab04}.  Constraint Programming is a framework that lends
itself very well to represent and reason about all of those elements
\comment{Ixtet citation?}, consequently, there has been a good amount
of work building automated planners that take advantage of CP
techniques.  The most common approach in constraint-based planning has
been to encode the entire planning problem as a CP problem, where
action choices and relationships are represented as variables and/or
constraints \comment {citations 158,519,539,556 from malik's book}.
The advantage of using a pure CP formulation is that standard CP
solvers can be then used to solve the planning problem, however, this
approach also has a couple of significant drawbacks:

@@

These drawbacks have been addressed by a small number of planning frameworks like Descartes \comment{citation 289,290 from malik's book}, IxTet \comment{citation  223 from Malik's book}, and CAIP (Constraint-Based Interval and Attribute Planning)\cite{mus94,frank2003}.
These frameworks take advantage of a CSP representation to deal with time and resources, at the same time maintaining an explicit representation of the elements relevant to planning (action choices, causal relationships, etc). This combination results in a planning approach that can deal with the type of constraints found in real-life problems, while allowing for intuitive problem descriptions and a natural way to express search algorithms and heuristics. \eu is an implementation of the CAIP framework. In CAIP, planning problems are specified in terms of:

\begin{enumerate}
	\item \textbf{Intervals}: entities that have a temporal scope (that is, a beginning and an  end in time) and a set of attributes. Intervals are used to represent actions and states in the planning domain. 
	\item \textbf{Variables and Constraints}: Variables represent Interval attributes and Constraints enable a direct representation of temporal, resource and any other the restrictions that a valid plan must comply with.
	\item \textbf{Domain Configuration Rules}: this is an explicit representation of the conceptual relationships between actions and states in the problem domain, for instance, for a Shopping Agent to be able to purchase a product, it must be at a location where the product is available.
\end{enumerate}

To generate plans, the CAIP framework uses a plan-space search approach \comment{cite malik's chapter 5}, where a partial plan is evolved until all open goals are achieved, and all inconsistencies are removed, the specific search algorithm used by \eu will be covered in detail below.

>>>>

{\scriptsize
  \begin{quote}
[Planning] \emph{is an abstract, explicit deliberation process that chooses and
organizes actions by anticipating their expected outcomes. This
deliberation aims at achieving as best as possible some prestated
objectives. Automated planning is an area of Artificial Intelligence
(AI) that studies this deliberation process computationally.} -- from
\textbf{Automated Planning Theory and Practice} by Ghallab, Nau and
Traverso \cite{ghallab04} 
\end{quote}
}

@@

Arc Consistency and other, more stringent consistency definitions can
be used to efficiently prove that a \textsf{CP} problem is
unsatisfiable. However, they generally cannot prove that a \textsf{CP}
problem is satisfiable and provide specific variable assignments that
constitute solutions. For that, search algorithms like global
backtracking \cite{hooker05} or local search are used; these use
consistency as an efficient way to prune the search space
\cite{cp06}. In theory, solving a \textsf{CP} problem is NP-Hard
\cite{ghallab04}, but often very efficient in practice using a number
of consistency and search algorithms that are well understood.

@@

The most common planning formulations use a propositional
representation, where the state of the world is represented by a set
of propositions (statements that can be true or false), and operators
change the truth values of these propositions \cite{gen87}. Although
these formulations are powerful and have allowed researchers to
develop numerous contributions in automated planning, there are many
classes of problem domains that are difficult to represent using this
formalism. In particular, it is hard to represent time, resources,
% mutual exclusion and concurrency using propositions
% \cite{ghallab04}. While CSP representations have traditionally had an
% edge in formulating and representing planning problems,
% % It is straightforward to represent and reason about all of
% % those elements using a CSP representation, as a result there has been
% % some work on doing automated planning while taking advantage of CSP
% % (TODO: ref). Traditionally, the entire planning problem is translated
% % into a CSP and then solved using traditional CSP methods, this
% leading to a formulation where action choices and relationships are
% represented as variables and/or constraints, there are at least two
% major drawbacks:
mutual exclusion and concurrency using propositions \cite{ghallab04}.
Constraint Programming is a framework that lends itself very well to
represent and reason about all of those elements \cite{ghallab94},
consequently, there has been a good amount of work building automated
planners that take advantage of CP techniques.  The most common
approach in constraint-based planning has been to encode the entire
planning problem as a CP problem, where action choices and
relationships are represented as variables and/or constraints
\cite{do01,vanbeek99,vossen99,wolfman99}.  The advantage of using a
pure CP formulation is that standard CP solvers can be then used to
solve the planning problem, however, this approach also has a couple
of significant drawbacks:

@@

These drawbacks have been addressed by a small number of planning
frameworks like \texttt{Descartes} \cite{joslin95,joslin96},
\texttt{IxTet} \cite{ghallab87,lemai04}, and CAIP (Constraint-Based
Interval and Attribute Planning)\cite{mus94,frank2003}.  These
frameworks take advantage of a CSP representation to deal with time
and resources, at the same time maintaining an explicit representation
of the elements relevant to planning (action choices, causal
relationships, etc). This combination results in a planning approach
that can deal with the type of constraints found in real-life
problems, while allowing for intuitive problem descriptions and a
natural way to express search algorithms and heuristics. \eu is an
implementation of the CAIP framework. In CAIP, planning problems are
specified in terms of:

\item \textbf{Intervals}: entities that have a temporal scope (that
  is, a beginning and an end in time) and a set of
  attributes. Intervals are used to represent actions and states in
  the planning domain.

\item \textbf{Variables and Constraints}: Variables represent Interval
  attributes and Constraints enable a direct representation of
  temporal, resource and any other the restrictions that a valid plan
  must comply with.

\item \textbf{Domain Configuration Rules}: this is an explicit
  representation of the conceptual relationships between actions and
  states in the problem domain, for instance, for a Shopping Agent to
  be able to purchase a product, it must be at a location where the
  product is available.
\end{enumerate}

To generate plans, the CAIP framework uses a plan-space search
approach \cite{ghallab04}, where a partial plan is evolved until all
open goals are achieved, and all inconsistencies are removed, the
specific search algorithm used by \eu will be covered in detail below.
